---
title: "p8105_hw5_hh2767"
author: "Haoran Hu"
date: "2018-11-5"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)

knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

#Problem 1

##Read in file names and files

In the following chunk, I will:

* Start with a dataframe containing all file names, using list.file function

* Use purrr::map to read in the data and save it as a new variable in the dataframe

```{r message=FALSE}
exp_files = list.files(".\\data\\data_exp") %>% 
  strsplit(split = " ") %>% 
  tibble() %>% 
  rename(., file_name = .) %>% 
  mutate(data = purrr::map(.x = file_name, ~read_csv(str_c(".\\data\\data_exp\\", .x)))) 

head(exp_files)
```

So far, I have created a dataframe called "files". It includes two columns:"file_name" and "data". The "file_name" column shows all the file names, and the "data" colume contains the data in each file corresponding to those file names. 

##Tidy the results

Next, I will:

* Show arms and IDs of subjects in the dataframe.

* Tidy the weekly observation data.

* Recode the data into informative forms. For example, changing "con" into "control".

```{r}
exp_data = 
  exp_files %>% 
  separate(file_name, into = c("arm", "subject_id"), sep = "_") %>% 
  separate(subject_id, into = c("subject_id", "remove"), sep = "\\.") %>% 
  select(-remove) %>% 
  mutate(., arm = recode(.$arm, con = "control", exp = "experiment")) %>% 
  unnest() %>% 
  gather(key = week, value = value, week_1:week_8) %>% 
  mutate(week = str_replace(week, "week_", " "),  
         subject = str_c(arm, "_", subject_id)) %>% 
  select(subject, arm, week, value)

str(exp_data)
  
```

The finel dataset is a `r nrow(exp_data)`(rows) * `r ncol(exp_data)`(cols) dataset. It contains four variables: 

* subject, which shows the ids of subjects. 

* arm, which shows whether a subject is in experimental arm or control arm

* week, which shows the time of an observation 

* value, which shows observation value

This dataset is a tidy dataset.

##Making a plot

```{r}
exp_data %>% 
  ggplot(aes(x = week, y = value, group = subject, color = arm)) + 
  labs(title = "Experiment observations on each subject over time", y = "Observation value") + 
  geom_line() +
  geom_point() +
  theme_bw()  + theme(legend.position = "bottom")

```

From the spaghetti plot, we can see that the observation values of subjects in experimental arm is higher than that of subjects in control arm. In addition, the observation values of subjects in experimental arm kept increasing over time, while the observation values of subjects in control arm remain stable. In other words, the difference between observation value of subjects in experimental arm and that of subjects in control arm was becoming greater over time.

#Problem 2

##Read and describe the dataset

```{r}

homicide = GET("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  content("raw") %>% 
  read_csv
str(homicide)
  
```

The raw dataset contains `r ncol(homicide)` variables and `r nrow(homicide)` observations. It contains information about `r nrow(homicide)` homicides occured in the US. The variables in this dataset are:

* uid: homicide id
* reported_date: reported date
* victim_last: last name of victim
* victim_first: first name of victim
* victim_race: race of victim
* victim_age: age of victim
* victim_sex: sex of victim
* city: city of the homicides
* state: state of the homicides
* lat: occurrence latitude
* lon: occurence longitude
* disposition: result of investigation

The location, time, and information of victims of each homicide are included in the dataset. The dataset also indicates whether the homicides are solved or not.

##Adding variables and tidying the dataset

In the following part, I will:
* create a sity_state variable which show the city and state of occurence
* summarize within cities to obtain the total number of homicides and the number of unsolved homicides

```{r}
homicide = homicide %>% 
  mutate(city_state = str_c(city, ",", state))

homicide_summary = homicide %>% 
  group_by(city_state) %>% 
  summarize(
    num_unsolved = sum(disposition %in% c("Open/No arrest", "Closed without arrest")),
         num_total = n()
    )
  
str(homicide_summary)
```

##Use prop.test for Baltimore

In the following chunk, I will:

* apply prop.test to estimate the proportion of unsolved homicide in Baltimore.

* apply broom::tidy, and pull the estimated proportion and confidence intervals from the resulting dataframe.

```{r}
 baltimore_homicide = homicide_summary %>% 
  filter(city_state == "Baltimore,MD")
  
baltimore_test = prop.test(baltimore_homicide$num_unsolved, baltimore_homicide$num_total) %>% 
  broom::tidy() 


tibble(
  city = "Baltimore,MD",
  'estimated proportion' = pull(baltimore_test, estimate),
  'confidence interval' = str_c("[",round(pull(baltimore_test, conf.low), 2),", ", round(pull(baltimore_test, conf.high), 2), "]")
) %>% 
  knitr::kable(digits = 2)
```

##Apply the process above to each of the cities

In this part, I will make use of purrr::map, purrr::map2, list columns and unnest to apply the process shown in the last part to each of the cities.

```{r}
city_homicide = function(unsolve, total){
  city_test = prop.test(unsolve, total) %>% 
    broom::tidy()
  tibble(
  'estimated proportion' = round(pull(city_test, estimate), 2),
  CI_low = round(pull(city_test, conf.low), 2), 
  CI_high = round(pull(city_test, conf.high), 2)
)
}

homicide_summary = homicide_summary %>% 
  mutate(homicide_estimate = purrr::map2(num_unsolved, num_total, city_homicide)) %>% 
  unnest()

unnest(homicide_summary)
```

Alternatively, if use purrr::map, we can get the same dataset, as shown below.

```{r}
# city_homicide = function(data, city){
#   city_data = data %>%
#     filter(city_state == city)
#   
#   city_test = prop.test(city_data$num_unsolved, city_data$num_total) %>% 
#     broom::tidy()
#   
#   tibble(
#   'estimated proportion' = round(pull(city_test, estimate), 2),
#   CI_low = round(pull(city_test, conf.low), 2), 
#   CI_high = round(pull(city_test, conf.high), 2)
# )
# }
# 
# homicide_summary = homicide_summary %>% 
# mutate(homicide_estimate = map(.x = homicide_summary$city_state, ~city_homicide(data = homicide_summary, city = .x))) %>% 
#   unnest()
# 
# str(homicide_summary)
```

#Making a plot

In this part, I will use geom_errorbar to make a plot that shows the estimates and CIs of proportion of unsolved homicides for each city. In the plot, cities will be organized according to the proportion of unsolved homicides.

```{r}
homicide_summary %>% 
  mutate(prop_unsolve = num_unsolved / num_total) %>% 
  arrange(prop_unsolve) %>% 
  #mutate(city_state = factor(city_state, levels = city_state)) %>% 
  mutate(city_state = forcats::fct_reorder(city_state, prop_unsolve)) %>% 
  ggplot(.) +
  geom_point(aes(x = city_state, y = `estimated proportion`), color = "brown1") +
  geom_errorbar( aes(x = city_state, ymin = CI_low, ymax = CI_high)) +
  labs(title = "Estimated proportion of unsolved homicides in each city", x = "City") +
  theme(axis.text.x = element_text(face = "plain", color = "black", size = 6.5, angle = 90), legend.position = "null")
```

